A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-11-10 related.tex
text added for reviewer 1 comment 1

The main intuition in pattern-based program repair methods is that bug fixes follow certain patterns. Thus, having a collection of common bug fix patterns is a crucial step for developing such repair tools. \cite{pan2009toward} analyzed seven large-scale widely used Java projects and obtained 27 common bug fix patterns. They used a bug fix pattern extractor tool to automatically parse and detect bug patterns within the bug fix hunks with less than seven statements. They ignored larger bug fix hunks as they tended to exhibit random changes and did not have observable meaningful patterns. Though they did the analysis on Java projects, their reported patterns were not specific to Java. \cite{martinez2015mining,martinez2012mining} exploited the frequency of observed patterns to introduce a heuristic patch searching method. In their empirical evaluation, they concluded that choosing repair actions probabilistically (weighted by frequency) can help with reducing the search space, hence creating a more effective repair tool.

>>>>

The main intuition in pattern-based program repair methods is that bug fixes follow certain patterns. Thus, having a collection of common bug fix patterns is a crucial step for developing such repair tools. Studying bug fix patterns can be traced back to 1975 when Enders et al introduced a classification of bugs that occur in DOS/VS operating system. This work contends that categorizing bug patterns can aid in uncovering error causes, fixing them, and preventing their recurrence. Flanagan et al. proposed MrSpidey, an interactive static debugger for Scheme (a dialect of Lisp). MrSpidey allows the programmer to browse program invariants and their derivations over error prone patterns (unsafe operators). The user can determine whether the error will actually occur, or if obtaining the correctness proof is unattainable due to the tool's limitations.

More recently, \cite{pan2009toward} analyzed seven large-scale widely used Java projects and obtained 27 common bug fix patterns. They used a bug fix pattern extractor tool to automatically parse and detect bug patterns within the bug fix hunks with less than seven statements. They ignored larger bug fix hunks as they tended to exhibit random changes and did not have observable meaningful patterns. Though they did the analysis on Java projects, their reported patterns were not specific to Java. \cite{martinez2015mining,martinez2012mining} exploited the frequency of observed patterns to introduce a heuristic patch searching method. In their empirical evaluation, they concluded that choosing repair actions probabilistically (weighted by frequency) can help with reducing the search space, hence creating a more effective repair tool.
